---
title: "Sample Graphs"
author: "Harsha"
date: "April 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

I am adding some of the possible graphs we can use in R using ggplot and plot_ly. 
```{r cars, warning= FALSE}
library(plotly);library(ggplot2)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
df <- diamonds[sample(1:nrow(diamonds), size = 2000),]
plot_ly(df, x = df$x, y = df$price, mode = "markers", color = df$cut, size = df$z) %>%
layout(title = "Scatter Plot -Diamonds")


```
```{r}
 ggplot(mtcars, aes(x = mtcars$gear, y = mtcars$hp))+
    geom_bar(
    aes(fill = mtcars$mpg), stat = "identity", color = "white",
    position = position_dodge(0.9)
    )+
     facet_wrap(~mtcars$vs)+ggtitle("Cars Milages Vs HP Vs Gear")
```

Mosaic Graphs can be used to give a visual representation for cross tabulation of categorical data. The data for these plots is usually generated using the 
xtabs functions in the vcd library.

```{r}
a <- xtabs( ~ gear+cyl+carb, mtcars)

mosaic(a, shade = TRUE, legend = TRUE)

```

A heatmap is basically a table that has colors in place of numbers. Colors correspond to the level of the measurement. It's useful for finding highs and lows and sometimes, patterns.
```{r}
attitude_matrix <- data.matrix(attitude)
heatmap(attitude_matrix, Rowv=NA,
        Colv=NA, col = cm.colors(256), scale="column", margins=c(5,10))
```


```{r}
studlon <- read.csv("D:\\My_Apps\\Data\\Student_Debt.csv")
studloc <- read.csv("D:\\My_Apps\\Data\\Stateloc.csv")

us.states <- subset()

df.merge <- inner_join(studlon,studloc, by =c("State" = "State"))

  ggplot(df.merge, aes(x = Lon, y = Lat, group = Rank)) + 
  geom_polygon(aes(fill = Avg_Debt_PP_Thousands)) + 
  expand_limits() + 
  theme_minimal()

```

