---
title: "Logistic Regression"
author: "Harsha"
date: "April 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Logistic regression 

Linear regression  assumes that the response variable Y is quantitative. However, in many situations we are dealing with qualitative response variables and we use Logistic regression in those cases. Generally, we will refer to these types of variables as categorical variables. For example: eye color is categorical since it has values like brown, blue, and green. Classification thereby involves assigning categorical variables to a specific class. Usually, we predict the probability of any observation belonging to a specific class.

There are many classification techniques, or classifiers, that could be used to predict a given qualitative response variables. Examples covered in this notebook include:

Logistic Regression
Linear Discriminant Analysis
K-nearest neighbors

```{r cars, echo = FALSE,warning=FALSE}
  adultincome <- read.csv("D:\\My_Apps\\Data\\adult.csv")
  library(ggplot2); library(gridExtra);library(plotly);library(ggplot2)
  attach(adultincome)  

  str(adultincome)

```

## Including Plots
We can see that these data have 48842 observations of 15 variables. Let's create a few diagnostic plots to get a sense of the data. 

```{r pressure,warning=FALSE}

adultincome <- subset(adultincome,(race %in% c('White','Black')) & (education %in% c('Masters','Bachelors','HS-grad','Assoc-voc','10th')))

 ggplot(adultincome, aes(x = education, y = age))+
    geom_bar(
    aes(fill = income), stat = "identity", color = "white",
    position = position_dodge(0.9)
    )+
     facet_wrap(~gender) 

plot_ly(y = ~ age, color = ~ education, type = "box")



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r,warning=FALSE}
glm(gender ~ age, data=adultincome, family='binomial')
```

